Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-30 paper/tex/introduction.tex
fix characterization of Mandelbaum08 and add CFHT Erben ref

Though the standard has long been for each galaxy in a photometric catalogue to have a \pz\ point estimate and Gaussian error bar, the nontrivial mapping between broad band fluxes and redshift renders this simplistic summary inadequate to quantify the uncertainty landscape by neglecting degenerate redshift solutions.
Far from a hypothetical situation, this degeneracy is a real consequence of the same deep imaging that enables larger galaxy catalogue sizes.
The lower luminosity and higher redshift populations captured by deeper imaging introduce major physical systematics to \pz s, among them the Lyman break/Balmer break degeneracy, that did not affect shallower large area surveys like the Sloan Digital Sky Survey \citep[\textsc{SDSS},][]{York:00} and Two Micron All Sky Survey \citep[\textsc{2MASS},][]{Skrutskie:06}.

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases from \citep{Mandelbaum:2008} to \citep{de_Jong:17}, provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.

>>>>

Though the standard has long been for each galaxy in a photometric catalogue to have a \pz\ point estimate and Gaussian error bar; however, as use in precision cosmology measurements became more prevalent there was a realization that point-estimate photo-$z$'s were inadequte \citep{mandelbaum:2008}.  The nontrivial mapping between broad band fluxes and redshift renders a simplistic point estimate inadequate to quantify the uncertainty landscape by neglecting degenerate redshift solutions.
Far from a hypothetical situation, this degeneracy is a real consequence of the same deep imaging that enables larger galaxy catalogue sizes.
The lower luminosity and higher redshift populations captured by deeper imaging introduce major physical systematics to \pz s, among them the Lyman break/Balmer break degeneracy, that did not affect shallower large area surveys like the Sloan Digital Sky Survey \citep[\textsc{SDSS},][]{York:00} and Two Micron All Sky Survey \citep[\textsc{2MASS},][]{Skrutskie:06}.

To fully characterize such physical degeneracies, photometric galaxy catalogue data releases, (e.~g.~\citet{Erben:2013}, \citet{de_Jong:17}), provided a more informative \pz\ data product, the \pz\ probability density function (PDF), that describes the redshift probability, commonly denoted as $p(z)$, as a function of a galaxy's redshift, conditioned on the observed photometry.
Early template-based methods such as \citet{Fernandezsoto:99} approximated the likelihood of photometry conditioned on redshift with the relative \chisq\ values of template spectra.
Not long after, Bayesian adaptations of template-based approaches such as \citet{Benitez:00} combined the estimated likelihoods with a prior to yield a posterior PDF of redshift conditioned on photometry.
While the first data-driven \pz\ algorithms yielded a point estimate, \citet{Firth:03} estimated a \pzpdf\ using a neural net with realizations scattered within the photometric errors.
